Is statistical significance a thing?

### 2018-04-05 doc.tex
add refs to bib; oikos note

\textbf{Venue:} \mk{My list, no input from PIs on this yet}. No idea... Forum in Trends in E and E: max 1200 words?
Note in The American Naturalist: max 3000 words? Perspectives article in Nature?

>>>>

\textbf{Venue:} \mk{My list, no input from PIs on this yet}. No idea... Forum in Trends in E and E: max 1200 words?
Note in The American Naturalist: max 3000 words? Perspectives article in Nature?
Oikos forum? \url{http://www.oikosjournal.org/authors/author-guidelines}: ``Proposals should be no more than half a page in length and should include statements about the novelty and need for the piece as well as suggestions with regard to which members of the editorial board would be most suited to evaluating the proposal.''
